### 2019-07-26 paper/paper.tex
Update paper.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INSERT PSEUDOCODE HERE IN TABLES OR FIGURES 2 and 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Why GlobalSearchRegression.jl is faster than existing alternatives?}
\label{sec:whygsreg}
\subsection{JULIA platform}
\label{subsub:juliaplat}

Despite some \verb GlobalSearchRegression.jl  specific features to be examined below, our all-subset-regression algorithm benefits from the well-known Julia language efficiency for High Performance Computing tasks.

\vspace{-2mm}

%%%%%%%%%%%%%%%%%% Table 2
\begin{table}[!h]
\centering
\tbl{Julia speed-up over STATA and R in basic functions}{
    \begin{tabular}{|l|c|c|}
    \hline
    Function & Speed-up over R & Speed-up over Stata \\
    \hline
    \hline
    recursion\_fibonacci & 251.28 & 76.92 \\
    \hline
    recursion\_quicksort & 32.36 & 48.54 \\
    \hline
    matrix\_multiply & 11.6 & 14.07 \\
    \hline
    iteration\_pi\_sum & 14.33 & 26.89 \\
    \hline
    matrix\_statistics & 7.65 & 44.92 \\
    \hline
    parse\_integers & 28.4 & 49.38 \\
    \hline
    userfunc\_mandelbrot & 175.44 & 368.42 \\
    \hline
    \hline
    Simple-Average & 74.44 & 89.88 \\
    \hline
    Weighted-Average & 12.15 & 22.01 \\
    \hline
    \multicolumn{3}{p{8.5cm}}{Note: Weighted-average were estimated as the Ratio between total execution time for R or Stata, and Julia's total execution time. Benchmarkings were obtained using a i7-4700MQ quad-core build, with 8 GiB of DDR3 1600 Mhz RAM, under Windows 8 and running Julia 1.1.0, Stata 15 and R %3.5.3}
    \end{tabular}
    }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INSERT PSEUDOCODE HERE  FIGURES 2 and 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
